Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-07 article/article.tex
Commit 2024-06-07 13:12

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Long term cloud enhancement events of global solar irradiance over Thessaloniki},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

@@

  \title{Long term cloud enhancement events of global solar irradiance
over Thessaloniki}
    \author[LAP]{Athanasios N. Natsis%
  \corref{cor1}%
  }
   \ead{natsisphysicist@gmail.com} 
    \author[LAP]{Alkiviadis Bais%
  %
  }
   \ead{abais@auth.gr} 
    \author[LAP]{Charikleia Meleti%
  %
  }
   \ead{meleti@auth.gr} 
      \affiliation[LAP]{
    organization={Laboratory of Atmospheric Physics, Physics Department,
Aristotle University of
Thessaloniki},city={Thessaloniki},postcode={54124},country={Greece},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{This is the first author footnote.}
    \fntext[2]{Another author footnote.}

@@

\hypertarget{intro}{%
\section{Intro}\label{intro}}

The shortwave solar irradiance, reaching Earth's surface, is the main
energy source of the atmosphere and the biosphere, and drives and
governs the climate \citep{Gray2010}. It has direct practical
application, in industries like energy and agricultural production. The
variability of its intensity, can cause difficulties in predicting the
yield, and designing the specifications of the appropriate equipment.
Significant portion of research has been focused on predicting the
renewable energy production in a fine timescale and in near real-time
(for a review see \citet{Inman2013}; \citet{Graabak2016}).

A big aspect of this variability is the interaction of GHI with the
clouds. In general, clouds absorb part of the solar irradiance, but
under certain conditions, can enhance the total shortwave irradiance
reaching the ground. This effect, can locally increase the observed GHI,
even higher than the expected clear sky irradiance {[}see references
therein{]}.

>>>>

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

@@

  \title{Long term cloud enhancement events of global solar irradiance
over Thessaloniki, Greece}
    \author[LAP]{Athanasios N. Natsis%
  \corref{cor1}%
  }
   \ead{natsisphysicist@gmail.com} 
    \author[LAP]{Alkiviadis Bais%
  %
  }
   \ead{abais@auth.gr} 
    \author[LAP]{Charikleia Meleti%
  %
  }
   \ead{meleti@auth.gr} 
      \affiliation[LAP]{
    organization={Laboratory of Atmospheric Physics, Physics Department,
Aristotle University of
Thessaloniki},city={Thessaloniki},postcode={54124},country={Greece},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{This is the first author footnote.}
    \fntext[2]{Another author footnote.}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The shortwave solar radiation, reaching Earth's surface, is the main
energy source of the atmosphere and the biosphere, and drives and
governs the climate \citep{Gray2010}. It has direct practical
application; in industries like energy and agricultural production. The
variability of its intensity; can impose difficulties in predicting the
yield; and in designing the specifications of the appropriate equipment.
Significant portion of research has been focused on predicting the
renewable energy production in a fine timescale and in near real-time
(for a review see \citet{Inman2013}; \citet{Graabak2016}).

An important aspect of the variability of solar radiation is its
interaction with the clouds. In general, clouds can attenuate a fraction
of solar irradiance, but under certain conditions, can lead to
enhancement of the global horizontal irradiance (GHI) reaching the
ground. This effect can locally increase the observed GHI to levels even
higher than the expected clear-sky irradiance \citep[ see references
therein]{Cordero2023, Vamvakas2020}.
